---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Frequently Used Functions

> 2017-04-05 배균섭 교수님 강의

자주 쓰는 함수 및 명령어에 대해 알아보겠습니다.

## Command

```{r code = readLines("R/Script20170405.R", encoding = "UTF-8"), eval = TRUE}
```


```{r, results = 'asis', echo = FALSE}
Freq <- read_excel("data-raw/R-Keyword-Functions-Freq-Essential.xlsx", 
    sheet = "Sheet1")
Freqlist <- bind_cols(Freq %>% select(1, 2) %>%  na.locf, Freq %>% select(-1, -2, Keyword = 3)) %>% 
    filter(!is.na(Essential)) %>% 
    mutate(Title = paste(Category, Subcategory)) %>% 
    mutate(Title = gsub("#|&", "-", Title)) %>% 
    #mutate(Keyword = gsub("\\[\\[", "\\\\[\\\\[", Keyword)) %>% 
    filter(Keyword != "[[") %>% 
    mutate(Title = factor(Title, ordered = FALSE, levels = unique(Title))) %>% 
    mutate(Comment = ifelse(is.na(Comment), "", Comment))

Freqfinal <- lapply(split(Freqlist, Freqlist[, "Title"]), 
       function(x) x %>% select(-Category, -Subcategory, -Title))
```

## The basics

```{r, echo = FALSE}
Datatableskdata <- NULL
for (i in c(1:11)) {
    knit_expanded <- paste0(#"\n\n### ", gsub("^.*- ", "", names(Freqfinal)[i]),
                            "\n\n```{r knitchunk", i,", results='asis', echo=FALSE}\n\n
                            knitr::kable(Freqfinal[[", i, "]], caption = names(Freqfinal)[",i,"], booktabs = TRUE, longtable = FALSE)\n\n
                            ```")
    Datatableskdata <- c(Datatableskdata, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = Datatableskdata, encoding = 'UTF-8'), collapse = '\n')`

## Common data structures

```{r, echo = FALSE}
Datatableskdata <- NULL
for (i in 12:15) {
    knit_expanded <- paste0(#"\n\n### ", gsub("^.*- ", "", names(Freqfinal)[i]), "\n",
                            "\n\n```{r knitchunk", i,", results='asis', echo=FALSE}\n\n
                            knitr::kable(Freqfinal[[", i, "]], caption = names(Freqfinal)[",i,"], booktabs = TRUE, longtable = FALSE)\n\n
                            ```")
    Datatableskdata <- c(Datatableskdata, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = Datatableskdata, encoding = 'UTF-8'), collapse = '\n')`


## Statistics

```{r, echo = FALSE}
Datatableskdata <- NULL
for (i in 16:20) {
    knit_expanded <- paste0(#"\n\n### ", gsub("^.*- ", "", names(Freqfinal)[i]), "\n",
                            "\n\n```{r knitchunk", i,", results='asis', echo=FALSE}\n\n
                            knitr::kable(Freqfinal[[", i, "]], caption = names(Freqfinal)[",i,"], booktabs = TRUE, longtable = FALSE)\n\n
                            ```")
    Datatableskdata <- c(Datatableskdata, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = Datatableskdata, encoding = 'UTF-8'), collapse = '\n')`


## Working with R 

```{r, echo = FALSE}
Datatableskdata <- NULL
for (i in 21:23) {
    knit_expanded <- paste0(#"\n\n### ", gsub("^.*- ", "", names(Freqfinal)[i]), "\n",
                            "\n\n```{r knitchunk", i,", results='asis', echo=FALSE}\n\n
                            knitr::kable(Freqfinal[[", i, "]], caption = names(Freqfinal)[",i,"], booktabs = TRUE, longtable = FALSE)\n\n
                            ```")
    Datatableskdata <- c(Datatableskdata, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = Datatableskdata, encoding = 'UTF-8'), collapse = '\n')`


## I/O

```{r, echo = FALSE}
Datatableskdata <- NULL
for (i in 24:26) {
    knit_expanded <- paste0(#"\n\n### ", gsub("^.*- ", "", names(Freqfinal)[i]), "\n",
                            "\n\n```{r knitchunk", i,", results='asis', echo=FALSE}\n\n
                            knitr::kable(Freqfinal[[", i, "]], caption = names(Freqfinal)[",i,"], booktabs = TRUE, longtable = FALSE)\n\n
                            ```")
    Datatableskdata <- c(Datatableskdata, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = Datatableskdata, encoding = 'UTF-8'), collapse = '\n')`
